Introducing ICBe: Very High Recall and Precision Event Extraction from Narratives about International Crises

### 2022-11-02 replication_paper/psrm_draft/ICBe_manuscript.Rmd
psrm prep

This work was supported by a grant from the Office of Naval Research [N00014-19-1-2491] and from the Charles Koch Foundation [20180481].

@@

Conflicts of Interests 
========================================
There are no conflicts of interest to disclose.

>>>>

This work was supported by a grant from the Office of Naval Research [N00014-19-1-2491] and from the Charles Koch Foundation [20180481]. The financial sponsors played no in the design, execution, analysis and interpretation of data, or writing of the study.

@@

Competing Interests Declaration 
========================================
The authors declare that there are no competing interestes.

### 2022-11-02 replication_paper/psrm_draft/ICBe_manuscript.tex
psrm prep

This work was supported by a grant from the Office of Naval Research
{[}N00014-19-1-2491{]} and from the Charles Koch Foundation
{[}20180481{]}.

@@

\hypertarget{conflicts-of-interests}{%
\section{Conflicts of Interests}\label{conflicts-of-interests}}

There are no conflicts of interest to disclose.

>>>>

This work was supported by a grant from the Office of Naval Research
{[}N00014-19-1-2491{]} and from the Charles Koch Foundation
{[}20180481{]}. The financial sponsors played no in the design,
execution, analysis and interpretation of data, or writing of the study.

@@

\hypertarget{competing-interests-declaration}{%
\section{Competing Interests
Declaration}\label{competing-interests-declaration}}

The authors declare that there are no competing interestes.
